WritingSSfiles

### 2019-08-12 CreateStockSynthesis.Rmd
Updates to poseidon

```{r readdata, echo=FALSE}
require(r4ss)
source("./config/sardine_config.R")

@@

```{r}
results <- get(load(atlantis_output_name))
devtools::load_all()
species=c(species)

#Sample all boxes
boxes <- unique(results$nums$polygon)

#Efficiency of the survey
effic <- data.frame(species=species, efficiency=eff_case)

# Assume uniform selectivity
sel<- data.frame(species=rep(species,length(age_classes)),
               agecl=age_classes,
              selex=sel_by_age)

#Sample survey - 3rd timestep simulates a summer survey
survey_out <- create_survey(dat=results$nums, time=survey_sample_full, species=species, boxes=boxes, effic=effic, selex=sel)

@@

#Sample fish for age composition
age_comp_data <- sample_fish(survey_out, highEffN)

@@

@@

#Sample survey biomass
survObsBiom <- sample_survey_biomass(dat=survey_out,cv=cv,wtAtAge)

@@

```{r}
catch_numbers <-  create_fishery_subset(dat = results$catch,
                                         time = fish_years,
                                         species = species,
                                         boxes = boxes)

@@

#Test writing CPUE in biomass
  stocksynthesis.data <- SS_write_ts(ss_data_list = stocksynthesis.data,
                ts_data = list(survObsBiom$atoutput[fish_years],
                  catch_total$catch[catch_total$time==fish_years]),
                CVs = c(CVs$survey,
                        CVs$fishery),
                data_years = list((survObsBiom$time[fish_years]-survey_sample_time)/timestep+1,             fish_years),
            sampling_month = list(rep(survey_month,nyears),
                                rep(fishing_month,nyears)),
                units = c("biomass","numbers"),
                data_type=c("CPUE","catch"),
                fleets = c(2,1))

@@

SS_writedat(stocksynthesis.data, outfile = paste0("./inst/extdata/",model_dir,
datfile_name),
                 overwrite=TRUE)
```

@@

Below we get the weight-length relationship parameters from atlantis, calculate h and R0 from Atlantis $\alpha$ and $\beta$ parameters, use the \code{calc_Z} function to back out natural mortality (M) from Atlantis, and use the survey length-at-age from Atlantis to estimate a growth curve.
```{r}
#Get biological parameters
biolprm <- results$biolprm
fgs <- results$fgs
li_a_use <- biolprm$wl[match(fgs$Code[match(species,fgs$Name)],biolprm$wl[, 1]), 2]/1000
li_b_use <- biolprm$wl[match(fgs$Code[match(species,fgs$Name)],biolprm$wl[, 1]), 3]

@@

>>>>

```{r readdata, echo=FALSE}
require(r4ss)
source("./config/CCConfig.R")
source("./config/census_spec.R")
source("./config/sardine_config.R")

@@

if(!file.exists(file.path(d.name, 
                          paste0("output", scenario.name, "run_truth.RData")))){
  #Store all loaded results into an R object
  results <- run_truth(scenario = scenario.name,
                     dir = d.name,
                     file_fgs = functional.groups.file,
                     file_bgm = box.file,
                     select_groups = species,
                     file_init = initial.conditions.file,
                     file_biolprm = biol.prm.file,
                     file_runprm = run.prm.file,
                     verbose = TRUE
  )
} else {
  results <- get(load(file.path(d.name,
                              paste0("output", scenario.name, "run_truth_all.RData"))))
}
results <- get(load(atlantis_output_name))
devtools::load_all()
species=c(species)
truth <- results

survey_testBall <- create_survey(dat = truth$biomass_ages,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

# make up a constant 0 cv for testing
surv_cv <- data.frame(species=survspp, cv=rep(0.0,length(survspp)))

# call sample_survey_biomass with a bunch of 1000s for weight at age
# in the code it multiplies atoutput by wtatage/1000 so this allows us to use
# biomass directly
wtage <- data.frame(species=rep(survspp, each=10),
                    agecl=rep(c(1:10),length(survspp)),
                    wtAtAge=rep(1000.0,length(survspp)*10))

surveyB_frombio <- sample_survey_biomass(survey_testBall, surv_cv, wtage)

#save for later use, takes a long time to generate
saveRDS(surveyB_frombio, file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))

# this uses result$nums and a new function to get survey index in numbers (abundance)

survey_testNall <- create_survey(dat = truth$nums,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

# as above, make up a constant 0 cv for testing
surv_cv <- data.frame(species=survspp, cv=rep(0.0,length(survspp)))

surveyN <- sample_survey_numbers(survey_testNall, surv_cv)

#save for later use, takes a long time to generate
saveRDS(surveyN, file.path(d.name, paste0(scenario.name, "surveyNcensus.rds")))

Natage <- readRDS(file.path(d.name, paste0(scenario.name, "natage_census_sard.rds")))

lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "lengthwt_census_sard.rds")))

len <- lengthwt_census_ss$natlength

wtage_ann <- lengthwt_census_ss$muweight %>%
  filter(time %in% annualmidyear)

@@

#Sample fish for age composition
age_comp_data <- sample_fish(survey_testBall, highEffN)
boxes <- unique(results$nums$polygon)

@@

saveRDS(ss_length_stdsurv, file.path(d.name, paste0(scenario.name, "lengthwt_census_sard.rds")))

@@

#Sample survey biomass
survObsBiom <- sample_survey_biomass(dat=survey_testBall,cv=cv,wtAtAge)

@@

```{r}
fish_years <- annualmidyear[fish_years]
catch_numbers <-  create_fishery_subset(dat = results$catch,
                                         time = fish_years,
                                         species = species,
                                         boxes = boxes)

@@

#Use .txt file output biomass instead
names(results$catch_all)[2] <- "Species"
catch_total <- filter(results$catch_all, Species==species) %>%
  filter(time %in% (fish_years+8))

#Test writing CPUE in biomass
  stocksynthesis.data <- SS_write_ts(ss_data_list = stocksynthesis.data,
                ts_data = list(survObsBiom$atoutput[fish_years],
                  catch_total$catch),
                CVs = c(CVs$survey,
                        CVs$fishery),
                data_years = list((survObsBiom$time[fish_years]-survey_sample_time)/timestep+1,             fish_years),
            sampling_month = list(rep(survey_month,nyears),
                                rep(fishing_month,nyears)),
                units = c("biomass","biomass"),
                data_type=c("CPUE","catch"),
                fleets = c(2,1))

@@

SS_writedat(stocksynthesis.data, outfile = paste0(d.name, "/inst/extdata/",model_dir,
datfile_name),
                 overwrite=TRUE)
```

@@

Below we get the weight-length relationship parameters from atlantis, calculate h and R0 from Atlantis $\alpha$ and $\beta$ parameters, use the \code{calc_Z} function to back out natural mortality (M) from Atlantis, and use the survey length-at-age from Atlantis to estimate a growth curve.
```{r}
#Get biological parameters

#Load needed inputs for biological parameters
source(here("config/CC1Config.R"))
#biological parameters
biolprm <- load_biolprm(dir = "C:/Users/chris/Documents/GitHub/atlantisom", file_biolprm = biol.prm.file)
d.name <- "C:/Users/chris/Documents/GitHub/atlantisom"
#functional groups
fgs <- results$fgs
runprm <- load_runprm(dir = d.name, file_runprm = run.prm.file)
YOY <- load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))
truenums_ss <- results$nums[results$nums$species==species,]

YOY_ss <- YOY %>%
  select(Time, "SAR.0")

fullresZ <- calc_Z(yoy = YOY_ss,
                   nums = truenums_ss,
                   fgs = fgs,
                   biolprm = biolprm,
                   toutinc = runprm$toutinc)

meanwt_spp <- ss_length_stdsurv$muweight %>% 
  filter(time>burnin) %>%
  group_by(agecl) %>%
  summarize(meanwt = mean(atoutput))
sardine.ctl <-r4ss::SS_readctl(paste0("./inst/extdata/",
model_dir,
ctlfile_name))
sardine.ctl <- SS_write_biol(sardine.ctl, biolprm, "SAR", Z = mean(fullresZ$atoutput), wtsage=meanwt_spp)

li_a_use <- biolprm$wl[match(fgs$Code[match(species,fgs$Name)],biolprm$wl[, 1]), 2]/1000
li_b_use <- biolprm$wl[match(fgs$Code[match(species,fgs$Name)],biolprm$wl[, 1]), 3]

#maturity ogive
#check what R0 is

@@

#Add a call here to plot output
